---
params:
  title:  "Resume"
  author: "Benjamin Wolfe"
  date:   !r Sys.Date()
title:  "`r params$title`"
author: "`r params$author`"
date:   "`r params$date`"
output:
  html_document:
    css: css/custom.css
    includes:
      in_header: headers.html
---

```{r notes, eval=FALSE, include=FALSE}
# resume created with pagedown:
install.packages("pagedown")

# to serve (does not render properly otherwise):
servr::httw(
  dir     = "paged-js",
  watch   = "paged-js",
  pattern = "\\.html$",
  daemon  = TRUE
)
```

```{r setup, echo=FALSE, message=FALSE}
library(stringr)
library(magick)
library(here)
```

```{js, echo=FALSE}
// wait for an element to exist: https://gist.github.com/chrisjhoughton/7890303
// this became necessary for the workaround below when I added fontawesome
let wait_for_element = function(selector, callback) {
  if (jQuery(selector).length) {
    callback();
  } else {
    setTimeout(function() {
      wait_for_element(selector, callback);
    }, 100);
  }
};

// workaround: viewer settings keep getting overwritten by paged.js
// this removes the offending CSS when the page loads
$('document').ready( function() {

  // strings we'll be fixing
  const delete_this = 
    'background:'         + '0 0!important;' + 
    '-webkit-box-shadow:' + 'none!important;' + 
    'box-shadow:'         + 'none!important';
  const and_replace_this =
    'body{'
      + 'font-family:'      + '"Helvetica Neue",Helvetica,Arial,sans-serif;'
      + 'font-size:'        + '14px;'
      + 'line-height:'      + '1.42857143;'
      + 'color:'            + '#333;'
      + 'background-color:' + '#fff'
    + '}';
  const with_this =
    'body{'
      + 'font-family:' + '"Helvetica Neue",Helvetica,Arial,sans-serif;'
      + 'font-size:'   + '14px;'
      + 'line-height:' + '1.42857143;'
      + 'color:'       + '#333'
    + '}';

  const selector = 
      'head > style'
    + ':contains("base64")'
    + ':not(:contains("--pagedjs-width"))'

  wait_for_element(selector, function() {
    // this should only match one <style> element
    let crazy_long_style_element = $(selector);
    
    // perform the incision
    const new_css = crazy_long_style_element[0]
      .innerText
      .replace(delete_this, '')
      .replace(and_replace_this, with_this);
  
    // out with the old, in with the new
    crazy_long_style_element.remove();
    $('head')
      .append(
        '<style'
        + ' type="text/css"'
        + ' data-pagedjs-inserted-styles="true"'
        + '>'
          + new_css
      + '</style>'
      );
  });
});
```

```{css, echo=FALSE}
a[href]:after { /* override weird href behavior */
  display: none !important;
}

#header { display: none; }

.banner {
  height: 5em;
  margin-block-start: 0.5em;
  display: flex;
  justify-content: space-between;
}
.banner .column {
  width: 32%;
  line-height: 1em;
}
.banner .center {
  font-size: 1.8em;
  font-weight: bold;
  text-align: center;
  padding-block-start: 0.4em;
}
.banner .left,
.banner .right {
  padding-block-start: 0.8em;
  line-height: 1.25em;
}
.banner .left {
  text-align: left;
}
.banner .right {
  text-align: right;
}

.intro {
  width: 100%;
  margin-block-start: 0.5em;
  margin-block-end: 1em;
  text-align: center;
}
.intro p {
  margin-block-end: 0em;
}

.meat {
  width: 100%;
  display: flex;
  justify-content: space-between;
}
.meat .left {
  width: 60%;
  padding-inline-start: 0.6em;
  padding-inline-end: 1.5em;
  margin-block-start: -0.7em;
}
.meat .left h3.employer {
  font-size: 1.25em;
  margin-block-start: 1.2em;
  margin-block-end: 0.25em;
}
.meat .left h4.timing {
  font-size: 1em;
  margin-block-start: 0em;
  margin-block-end: 1em;
}
.meat .left ul,
.meat .left p {
  font-size: 0.85em;
}

.meat .left .bottom h4 {
  font-size: 1em;
  margin-block-start: 1.2em;
  margin-block-end: 0.8em;
}
.meat .left .bottom ul,
.meat .left .bottom p {
  font-size: 0.85em;
}
.meat .left .bottom ul {
  padding-inline-start: 1.5em;
}
.meat .left .bottom li {
  list-style-type: disc;
}

.meat .sidebar {
  width: 40%;
}
.meat .sidebar img {
  padding-inline-end: 1em;
  padding-block-start: 1em;
  margin-block-end: 1.5em;
}
.meat .sidebar h4 {
  font-size: 1em;
  margin-block-start: 1.2em;
  margin-block-end: 0.8em;
}
.meat .sidebar ul,
.meat .sidebar p {
  font-size: 0.85em;
}
.meat .sidebar ul {
  padding-inline-start: 1.5em;
}
.meat .sidebar li {
  list-style-type: disc;
}

.footer {
  width: 100%;
  display: flex;
  justify-content: space-between;
}
.footer .left {
  width: 60%);
}
.footer .sidebar {
  width: 40%;
}
.footer .sidebar h4 {
  font-size: 1em;
  margin-block-start: 0em;
  margin-block-end: 1em;
}
.footer .sidebar ul,
.footer .sidebar p {
  font-size: 0.85em;
}
.footer .sidebar ul {
  padding-inline-start: 1.5em;
}
.footer .sidebar li {
  list-style-type: disc;
}
```

<div class="page">
  <div class="banner">
  <div class="column left"><i class="fas fa-paper-plane"></i><a href="mailto:benjamin.e.wolfe@gmail.com">benjamin.e.wolfe@gmail.com</a>  
  <i class="fas fa-mobile-alt"><a href="tel:202-709-6533"></i>202.709.6533</a>
  <!-- end banner left -->
  </div>
  <div class="column center">`r str_to_upper(params$author)`
  <!-- end banner center -->
  </div>
  <div class="column right">[linkedin.com/in/BenjaminWolfe](https://www.linkedin.com/in/BenjaminWolfe)<i class="fab fa-linkedin"></i>
  [\@BenjaminWolfe](https://twitter.com/BenjaminWolfe)<i class="fab fa-twitter"></i>
  <!-- end banner right -->
  </div>
<!-- end banner -->
</div>

<div class="intro">
Analytics leader with 12 years experience.
Collaborative leader, innovator, thoughtful problem solver,

articulate communicator, and champion of excellence in analytics.
Looking to explore new challenges with you!
<!-- end intro -->
</div>

<div class="meat">
<div class="left">

### Esurance {.employer}
#### October 2011--current {.timing}

_CoverageMyWay™_.
Built a patent-pending, award-winning recommendation engine
from concept through rollout in 43 states
and oversaw the design and deployment of A/B tests.
CoverageMyWay suggests coverage packages and add-ons in the online quote flow.
Coordinated with disparate groups:
product management, legal compliance, copywriting, UX design, dev, and QA.

_Management_.
Led 2 teams consecutively over 6 years:
one built from the ground up, one acquired;
one managed in person, one remote.
Hired and mentored 6 data scientists / analysts
and cleared the way for 8 promotions.
Established a bi-weekly "Analytics Masterclass" to learn from our work.

_Analytics Ecosystem_.
Implemented [Heap Analytics](https://heap.io/)
for existing customers' clickstream traffic;
defined metrics and advocated for usage among partners.
Championed analytics best practices and tools:
[Jira](https://www.atlassian.com/software/jira) for workflow management,
[git](https://git-scm.com/) and [Bitbucket](https://bitbucket.org/product)
for version control,
full access to [Tableau Server](https://www.tableau.com/products/server)
for dashboarding.
Created an internal CX Analytics blog, a code cookbook,
and an internal R package repository.

_Deep-Dives_.
Analyzed issues of relevance to customers and CX stakeholders.
What DOI regulations cause purchasers the most friction?
What transactions are customers unable to complete themselves?
How will upcoming rate activity affect customer loyalty?
What can we do about it?
Explored data, recommended KPIs, wrote ETL jobs, designed dashboards,
shared learnings.

### Farmers Insurance Group {.employer}
#### October 2006--October 2011 {.timing}

_Automated reporting_.
Ran all recruitment and promotion tracking for regional marketing office.
Work initially involved heavy Excel usage exclusively.
Consolidated data back-end first to MS Access and then to MS SQL Server;
automated repetitive tasks with VBA.
Also consulted on nationwide projects.

_Agency and District Growth Dashboards_.
This company-wide initiative gathered a host of previously disconnected KPIs
into 360° views of the agent and district.
I researched the data sources and providers,
documented and conveyed findings to leadership,
and orchestrated and coded all data flows.

<div class="bottom">
#### Technical
* Expert: R, SQL, Tableau, Excel
* R: [tidyverse][6], [devtools][7], [pkgdown][8],
  [blogdown][9], [bookdown][10], [drat][11], [TravisCI][12]
* SQL: T-SQL, PL/SQL, PostGreSQL, Redshift, Hadoop, Hive

#### Published Work
* [Signs][3] (see [CRAN][4]) solves a simple problem of mathematical typography

#### Other
* Languages: English (native), Spanish (fluent)
* [CliftonStrengths][5]: Learner, Maximizer, Input, Connectedness, Intellection

<!-- end bottom of meaty left -->
</div>
<!-- end meaty left -->
</div>
<div class="sidebar">
```{r timeline-magick, echo=FALSE}
timeline <- image_read(here("images/timeline-1.png"))
image_trim(timeline)
```

#### Education
* Wheaton College, Wheaton, Illinois
* Bachelor of Arts in Spanish and Philosophy
* Graduated with honors; advanced studies in Mexico

#### Patent Pending & Awards
Co-inventor:
Apparatus & Method for Supplying Personalized Insurance Quotes.
US Patent Application 14/681,931, filed April 8, 2015. 

[CoverageMyWay][1]™ was 1 of 8
[InformationWeek Elite 100 Business Innovation Award][2] winners in 2015,
and won Esurance a place in the Elite 100 in 2016 as well.

<!-- end meaty sidebar -->
</div>
<!-- end meat -->
</div>

<div class="footer">
<div class="left">
<!-- end footer left -->
</div>
<div class="sidebar">
<!-- end footer sidebar -->
</div>
<!-- end footers -->
</div>
<!-- end page -->
</div>

[1]: https://web.archive.org/web/20160218214238/https://blog.esurance.com/esurance-introduces-coverage-my-way/
[2]: https://www.informationweek.com/strategic-cio/executive-insights-and-innovation/esurance-puts-analytics-closer-to-the-customer/d/d-id/1319843
[3]: https://benjaminwolfe.github.io/signs/
[4]: https://cran.r-project.org/web/packages/signs
[5]: https://www.gallup.com/cliftonstrengths
[6]: https://www.tidyverse.org/
[7]: https://devtools.r-lib.org/
[8]: https://pkgdown.r-lib.org/
[9]: https://bookdown.org/yihui/blogdown/
[10]: https://bookdown.org/yihui/bookdown/
[11]: https://github.com/eddelbuettel/drat
[12]: https://travis-ci.org/
