---
params:
  title:  "Resume"
  author: "Benjamin Wolfe"
  date:   !r Sys.Date()
title:  "`r params$title`"
author: "`r params$author`"
date:   "`r params$date`"
output:
  html_document:
    css: ["css/page.css", "css/classes.css"]
    includes:
      in_header: headers.html
---

```{r notes, eval=FALSE, include=FALSE}
# resume was created with paged.js,
# inspired by the `pagedown` resume template:
install.packages("pagedown")

# to serve locally (may not render properly otherwise):
servr::httw(
  dir     = "paged-js-2021",
  watch   = "paged-js-2021",
  pattern = "\\.html$",
  daemon  = TRUE
)
```

```{r setup, echo=FALSE, message=FALSE}
library(stringr)
```

```{js, echo=FALSE}
// wait for an element to exist: https://gist.github.com/chrisjhoughton/7890303
// this became necessary for the workaround below when I added fontawesome
let wait_for_element = function(selector, callback) {
  if (jQuery(selector).length) {
    callback();
  } else {
    setTimeout(function() {
      wait_for_element(selector, callback);
    }, 100);
  }
};

// workaround: viewer settings keep getting overwritten by paged.js
// this removes the offending CSS when the page loads
$('document').ready( function() {

  // strings we'll be fixing
  const delete_this = 
    'background:'         + '0 0!important;' + 
    '-webkit-box-shadow:' + 'none!important;' + 
    'box-shadow:'         + 'none!important';
  const and_replace_this =
    'body{'
      + 'font-family:'      + '"Helvetica Neue",Helvetica,Arial,sans-serif;'
      + 'font-size:'        + '14px;'
      + 'line-height:'      + '1.42857143;'
      + 'color:'            + '#333;'
      + 'background-color:' + '#fff'
    + '}';
  const with_this =
    'body{'
      + 'font-family:' + '"Helvetica Neue",Helvetica,Arial,sans-serif;'
      + 'font-size:'   + '14px;'
      + 'line-height:' + '1.42857143;'
      + 'color:'       + '#333'
    + '}';

  const selector = 
      'head > style'
    + ':contains("base64")'
    + ':not(:contains("--pagedjs-width"))'

  wait_for_element(selector, function() {
    // this should only match one <style> element
    let crazy_long_style_element = $(selector);
    
    // perform the incision
    const new_css = crazy_long_style_element[0]
      .innerText
      .replace(delete_this, '')
      .replace(and_replace_this, with_this);
  
    // out with the old, in with the new
    crazy_long_style_element.remove();
    $('head')
      .append(
        '<style'
        + ' type="text/css"'
        + ' data-pagedjs-inserted-styles="true"'
        + '>'
          + new_css
      + '</style>'
      );
  });
});
```

<div class="page">
  <div class="basics">
  <div class="column left"><i class="fas fa-paper-plane"></i><a href="mailto:benjamin.e.wolfe@gmail.com">benjamin.e.wolfe@gmail.com</a>  
  <i class="fas fa-mobile-alt"><a href="tel:202-709-6533"></i>202.709.6533</a>
  <!-- end basics left column -->
  </div>
  <div class="column center">`r str_to_upper(params$author)`
  <!-- end basics center column -->
  </div>
  <div class="column right">[linkedin.com/in/BenjaminWolfe][li]<i class="fab fa-linkedin"></i>
  [\@BenjaminWolfe][bw]<i class="fab fa-twitter"></i>
  <!-- end basics right column -->
  </div>
<!-- end basics -->
</div>

<div class="summary">
Analytics leader with 12 years experience.
Curious learner, supportive manager, articulate communicator,

collaborative problem solver, and champion of excellence in analytics.
Looking to explore new challenges with you!
<!-- end summary -->
</div>

<div class="details">
<div class="left">

<div class="flex-container">
<div class="flex-child">
### Munich Re Digital Partners {.employer}
#### January 2020--current {.timing}
</div><div class="flex-child">
##### Data Scientist {.titles}
</div></div>

_Data Product Management_.
Balanced the strategy, governance and implementation of all things data-related;
facilitated conversations among all impacted partners and internal stakeholders.
Established best practices and reduced technical debt.

_Solutions Design_.
Developed a rating engine used by non-technical stakeholders.

_Data Engineering_.
Wrote, productionalized, and maintained data pipelines.

<div class="flex-container">
<div class="flex-child">
### Esurance {.employer}
#### October 2011--December 2019 {.timing}
</div><div class="flex-child">
##### Sr. Marketing Analyst; Manager, Data Science; Manager, CX Analytics; Lead CX Analyst {.titles}
</div></div>

_Innovation_.
Built a patent-pending, award-winning recommendation engine
from concept through rollout in 43 states;
oversaw the design and deployment of A/B tests.
CoverageMyWay™ suggested coverage packages and add-ons in the online quote flow.
My team and I coordinated cross-functionally with insurance product management,
legal compliance, copywriting, UX design, development, and QA.

_Leadership_.
Had the pleasure of leading 2 talented teams over 6 years.
One was in person, one remote.
Hired and onboarded 6 data scientists and analysts, mentored 10,
advocated successfully for 8 promotions.
Championed consistent data science best practices:
version control, reproducibility, peer review, documentation,
a code cookbook and style guide, and an enterprise R package.

_Customer Experience_.
Set up customer listening posts to watch for pain points:
surveys, clickstream traffic monitoring, social media and public reviews.
Analyzed issues of relevance to customers and CX stakeholders,
like sources of friction, drivers of call volume,
and the expected impact of planned rate increases.

<div class="flex-container">
<div class="flex-child">
### Farmers Insurance Group {.employer}
#### October 2006--October 2011 {.timing}
</div><div class="flex-child">
##### Marketing Analyst {.titles}
</div></div>

_Reporting_.
Ran all recruitment and promotion tracking for a regional marketing office
before graduating to national projects.
Automated spreadsheets, web-scraping data collection, and email campaigns.

_Data Project Lead_.
Our initiative gathered several critical KPIs
into a broad, integrated view of the agent and district.
I researched data sources and providers,
conveyed findings to executive leadership,
and orchestrated & coded all data flows.

<div class="bottom">
#### Published Work
* The [signs][signs] package on [CRAN][cran] solves a problem
  of mathematical typography

#### Education
* Wheaton College, Wheaton, Illinois
* Bachelor of Arts in Spanish and Philosophy
* Graduated with honors; advanced studies in Mexico

<!-- end bottom of details left column -->
</div>
<!-- end details left column -->
</div>
<div class="sidebar">

#### Technical
* _Web Frameworks_: Hugo, Django, Flask
* _Web Analytics_: Heap Analytics, GA
* _Data Science, ML, ETL_: Tidymodels, Tidyverse, Pandas/Numpy, Airflow, Docker
* _Data Visualization_: Tableau, Looker, Shiny
* _Databases_: Snowflake, Redshift, SQL Server
* _Rules Engines_: JBoss Drools
* _Languages_: Python, R, SQL, HTML/CSS/JS/Sass

#### Patent Pending & Awards
Co-inventor:
Apparatus & Method for Supplying Personalized Insurance Quotes.
US Patent Application 14/681,931, filed April 8, 2015. 

[CoverageMyWay][cmw]™ was 1 of 8
[InformationWeek Elite 100 Business Innovation Award][infowk] winners in '15
and won Esurance a place in the Elite 100 in '16.

#### Spoken Languages
* English (native)
* Spanish (fluent)

#### Credits
CV created with [paged.js][pagedjs], inspired by RStudio's [pagedown][pagedown] package.

<!-- end details sidebar column -->
</div>
<!-- end details -->
</div>
<!-- end page -->
</div>

[li]: https://www.linkedin.com/in/BenjaminWolfe
[bw]: https://twitter.com/BenjaminWolfe
[signs]: https://benjaminwolfe.github.io/signs/
[cran]: https://cran.r-project.org/web/packages/signs
[cmw]: https://web.archive.org/web/20160218214238/https://blog.esurance.com/esurance-introduces-coverage-my-way/
[infowk]: https://www.informationweek.com/strategic-cio/executive-insights-and-innovation/esurance-puts-analytics-closer-to-the-customer/d/d-id/1319843
[pagedjs]: https://gitlab.pagedmedia.org/tools/pagedjs
[pagedown]: https://github.com/rstudio/pagedown
